---
fontsize: 12pt
geometry: margin=0.50in
subparagraph: yes
params: 
    title: "title"
    date:  "0000-00-00"
title: "`r params$title`"
date:  "`r params$date`"
header-includes:
   - \usepackage{titlesec}
   - \usepackage{array}
   - \usepackage{makecell}
   - \usepackage{booktabs}
   - \usepackage{float}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
    toc: false
    keep_tex: no
    latex_engine: xelatex
---

\titleformat{\section}{       \fontsize{26pt}{10pt}\selectfont}{}{0em}{}
\titleformat{\subsection}{    \fontsize{16pt}{10pt}\selectfont}{}{0em}{}
\titleformat{\subsubsection}{ \fontsize{12pt}{10pt}\selectfont}{}{0em}{}
\titleformat{\paragraph}{     \fontsize{ 8pt}{ 8pt}\selectfont}{}{0em}{}
\titleformat{\subparagraph}{  \fontsize{ 6pt}{ 6pt}\selectfont}{}{0em}{}

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(png)
library(grid)
library(dplyr)
library(ggplot2)
library(kableExtra)
options(stringsAsFactors = FALSE)
```

```{r, echo=FALSE, results='asis'}
if(nrow(LTRsampleTable) > 0){
  cat('The table below shows the unique LTR sequences (primer bit + LTR bit) found in the run metadata\n')
  cat('whereas the following table shows the prevlence of different leader sequences.\n')
  cat('\n\\vspace{0.5cm}\n')
  cat(kable(LTRsampleTable, 'latex', linesep = "", booktabs = T) %>% kable_styling(font_size = 10))
}
```


\vspace{0.5cm}

```{r, echo=FALSE, warning=FALSE}
ppNum <- function(n){ if(is.na(n)) return('na'); format(n, big.mark=",", scientific=FALSE, trim=TRUE) }

d <- counts
if(length(d) == 0) d <- data.frame()

if(length(d) >= 2){
  d[,1] <- cell_spec(d[,1], monospace = TRUE)
  d[,2] <- ppNum(d[,2])
}

if(length(d) >= 4){
  d[,3] <- cell_spec(d[,3], monospace = TRUE)
  d[,4] <- ppNum(d[,4])
}

if(length(d) >= 6){
d[,5] <- cell_spec(d[,5], monospace = TRUE)
d[,6] <- ppNum(d[,6])
}

kable(d, "latex",  linesep = "", booktabs = T, escape = FALSE) %>% 
  kable_styling(latex_options = "scale_down", font_size = 7) 
```

\newpage

The plots below show a random sampling of `r ppNum(readSamplePlotN)` unique reads from R1 and R2 respectively.  

\vspace{0.5cm}

```{r, echo=FALSE, warning=FALSE, dev='png', fig.height=4.5, dpi=150}
R1plot
```

\vspace{0.5cm}

```{r, echo=FALSE, warning=FALSE, dev='png', fig.height=4.5, dpi=150}
R2plot
```

\newpage

```{r, echo=FALSE, results='asis'}
if(nrow(runStats) > 0){
  cat('\nThe table below is a summary of intSiteCaller stages and called sites. Site counts are likely exaggerated because of alignment and sequencing errors which are corrected during subsequent analyses.  \n')
  cat('\n\\vspace{0.5cm}\n')

  cat(kable(runStats, "latex",  linesep = "", booktabs = T) %>% kable_styling( font_size = 8))

  cat('\n\\newpage')
}
```


```{r, echo=FALSE, results='asis'}
if(nrow(controlSites) > 0){
  cat('\nThe table below shows the reads counts and estimated abundances of recovered standardized control sites.  \n')
  cat('\n\\vspace{0.5cm}\n')
  cat(kable(controlSites, "latex", linesep = "", booktabs = T)  %>% kable_styling(font_size = 10)) 
  cat('\n\\newpage')
}
```



