---
fontsize: 12pt
geometry: margin=0.50in
subparagraph: yes
params: 
    title: "title"
    date:  "0000-00-00"
title: "`r params$title`"
date:  "`r params$date`"
header-includes:
   - \usepackage{titlesec}
   - \usepackage{array}
   - \usepackage{makecell}
   - \usepackage{booktabs}
   - \usepackage{float}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
    toc: false
    keep_tex: no
    latex_engine: xelatex
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(vegan)
library(knitr)
library(xtable)
library(ggforce)
library(gridExtra)
library(RColorBrewer)
library(grDevices)
library(png)
library(grid)
library(pander)
library(tidyverse)
library(kableExtra)
options(stringsAsFactors = FALSE)

```

\titleformat{\section}{       \fontsize{26pt}{10pt}\selectfont}{}{0em}{}
\titleformat{\subsection}{    \fontsize{16pt}{10pt}\selectfont}{}{0em}{}
\titleformat{\subsubsection}{ \fontsize{12pt}{10pt}\selectfont}{}{0em}{}
\titleformat{\paragraph}{     \fontsize{ 8pt}{ 8pt}\selectfont}{}{0em}{}
\titleformat{\subparagraph}{  \fontsize{ 6pt}{ 6pt}\selectfont}{}{0em}{}

# Summary  

No integration sites were recovered from any patient samples.

\vspace{1.0cm}

# Sample Summary  

The table below decribes the samples analyzed with the INSPIIRED pipeline.  

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Add VCN
summaryTable$VCN <- sampleData[match(summaryTable$GTSP, sampleData$SpecimenAccNum),]$VCN

# "scale_down", 
cat(kable(summaryTable, "latex", linesep = "", booktabs = T) %>% kable_styling(latex_options = c("hold_position")))
```

# Methods

All coordinates are on human genome draft hg38.

Detailed methods can be found these publications:  
- Bioinformatics. 2012 Mar 15; 28(6): 755–762.   
- Mol Ther Methods Clin Dev. 2017 Mar 17; 4: 17–26.  
- Mol Ther Methods Clin Dev. 2017 Mar 17; 4: 39–49.  
  
Analysis software:  
- INSPIIRED v1.1  (http://github.com/BushmanLab/INSPIIRED)  
 
Report generation software:  
- subjectReport v0.1 (http://github.com/everettJK/geneTherapySubjectReport)  






